Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-18 arxiv/tools.tex
appendix

The following simple resolvent identities are important tools for our proof. Recall that the resolvent minors have been defined in Definition \ref{defn_Minor}.
\begin{lemma}\label{lemm_resolvent}
We have the following resolvent identities.
\begin{itemize}
\item[(i)]
For $i\in \mathcal I_1$ and $\mu\in \mathcal I_1\cup \cal I_2$, we have
\begin{equation}
\frac{1}{G_{ii}} =  - z - \left( {AG^{\left( i \right)} A^\top} \right)_{ii} ,\quad  \frac{1}{{G_{\mu \mu } }} =  - 1  - \left( {A^\top  G^{\left( \mu  \right)} A} \right)_{\mu \mu }.\label{resolvent2}
\end{equation}

 \item[(ii)]
 For $i\in \mathcal I_1$, $\mu \in \mathcal I_1\cup \cal I_2$, $a\in \cal I\setminus \{i\}$ and $b\in \cal I\setminus \{ \mu\}$, we have
\begin{equation}
G_{ia}   = -G_{ii}  \left( AG^{\left( {i} \right)} \right)_{ia},\quad  G_{\mu b }  = - G_{\mu \mu }  \left( A^\top  G^{\left( {\mu } \right)}  \right)_{\mu b }. \label{resolvent3}
\end{equation}
%For $i\in \mathcal I_1$ and $\mu\in \mathcal I_2$, we have
%\begin{equation}\label{resolvent6}
%\begin{split}
% G_{i\mu } =  -G_{ii}  \left( WG^{\left( {i} \right)} \right)_{i\mu}, \quad G_{\mu i}= -G_{\mu\mu}\left( W^\top G^{(\mu)}\right)_{\mu i}. %\left( { - Y_{i\mu }  +  {\left( {YG^{\left( {i\mu } \right)} Y} \right)_{i\mu } } } \right) . %, \ \  G_{\mu i}  = G_{\mu \mu } G_{ii}^{\left( \mu  \right)} \left( { - Y_{\mu i}^\top  + \left( {Y^\top  G^{\left( {\mu i} \right)} Y^\top  } \right)_{\mu i} } \right).
%\end{split}
%\end{equation}

@@

\begin{fact}\label{fact_minv}
	In the setting of Theorem \ref{thm_many_tasks}, with high probability over the randomness of $X$, we have that
	\begin{enumerate}
		\item When $n / p$ converges to $\rho > 1$, the sample covariance matrix $\frac{X^{\top}X}{n}$ is of full rank.
		\item The singular values of $Z^{\top}Z$ are greater than $(\sqrt{n} - \sqrt{p})^2 - n \cdot p^{-c_{\varphi}}$ and less than $(\sqrt{n} + \sqrt{p})^2 + n \cdot p^{-c_{\varphi}}$, cf. \citet[Theorem 2.10]{isotropic} and \citet[Lemma 3.12]{DY}.
	\end{enumerate}
\end{fact}

@@

\begin{lemma}[Lemma 3.8 of \cite{EKYY1} and Theorem B.1 of \cite{Delocal}]\label{largedeviation}
Let $(x_i)$, $(y_j)$ be independent families of centered and independent random variables, and $(A_i)$, $(B_{ij})$ be families of deterministic complex numbers. Suppose the entries $x_i$ and $y_j$ have variances at most $1$, and $ x_i$ and $ y_j$ satisfy the bounded support condition (\ref{eq_support}) for a deterministic parameter $q$. %with $q\le n^{-\phi}$ for a small constant $\phi>0$. 
Then we have the following bounds:
%for any fixed $\xi>0$, the following bounds hold with $\xi$-high probability:
\begin{align}
\Big| \sum_{i=1}^n A_i x_i \Big\vert \prec  q \max_{i} \vert A_i \vert+ \Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad &\Big\vert  \sum_{i,j=1}^n x_i B_{ij} y_j \Big\vert \prec q^2 B_d  + q n^{1/2}B_o +  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}},\label{eq largedev10}  \\
\Big\vert  \sum_{i=1}^n (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec q n^{1/2}B_d   , \quad &\Big\vert  \sum_{1\le i\ne j\le n} \bar x_i B_{ij} x_j \Big\vert  \prec qn^{1/2}B_o +  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev20} 
\end{align}
where $B_d:=\max_{i} |B_{ii} |$ and $B_o:= \max_{i\ne j} |B_{ij}|.$ Moreover, if the moments of $ x_i$ and $ y_j$ exist up to any order, then we have stronger bounds
\begin{align}
\Big\vert \sum_i A_i x_i \Big\vert \prec  \Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad  & \Big\vert \sum_{i,j} x_i B_{ij} y_j \Big\vert \prec  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev1} \\
 \Big\vert  \sum_{i} (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec  \Big( \sum_i |B_{ii} |^2\Big)^{1/2}  ,\quad & \Big\vert  \sum_{i\ne j} \bar x_i B_{ij} x_j \Big\vert  \prec \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} .\label{eq largedev2}
\end{align}
%\begin{align}
%\Big\vert \frac1{\sqrt{n}}\sum_i A_i x_i \Big\vert \prec  \frac{1}{\sqrt{n}}\Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad  & \Big\vert \frac1n\sum_{i,j} x_i B_{ij} y_j \Big\vert \prec  \frac{1}{n}\Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev1} \\
% \Big\vert  \frac1n \sum_{i} (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec \frac1{n}\Big( \sum_i |B_{ii} |^2\Big)^{1/2}  ,\quad & \Big\vert \frac1n\sum_{i\ne j} \bar x_i B_{ij} x_j \Big\vert  \prec  \frac{1}{n}\Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} .\label{eq largedev2}
%\end{align}
\end{lemma}

@@

\begin{corollary} \label{cor_largedeviation}
Let $Z\in \R^{n\times p}$ be a random matrix as in Assumption \ref{assume_rm}. Then for any deterministic vector $v\in \R^p$, we have that
\be\label{Zv_cor}\left|\|Zv\|^2- n\|v\|^2\right|\le  n^{1-c_\varphi} \|v\|^2\ee
with high probability.
\end{corollary}
 \begin{proof}
We introduce the truncated matrices $\wt Z$ with entries
$ \wt Z_{ij}:= \mathbf 1\left( |Z_{ij}|\le q \right)\cdot Z_{ij} $
for $q= n^{1/2-\frac{\varphi - 4}{2\varphi}}\log n$. By equation \eqref{Ptrunc}, we have that
\begin{equation}\label{XneX222}
\mathbb P(\wt Z= Z) =1-\OO ( (\log n)^{-\varphi}).
\end{equation}
Furthermore, by equation \eqref{meanshif} we have that
\be\label{meanshif222}
|\mathbb E  \wt  Z_{ij}| =\OO(n^{-3/2}), \quad  \mathbb E |\wt  Z_{ij}|^2 =1+ \OO(n^{-1}).
\ee
%From the first estimate in equation \eqref{meanshif}, we can also get a bound on the operator norm:
%\be\label{EZ norm222}\|\E \wt Z^{(1)}\|=\OO(n^{-1/2}) .
%\ee
Then we can centralize and rescale $\wt Z$ as $ \wh Z:=\frac{\wt Z - \E \wt Z }{ (\E|\wt Z_{11}|^2)^{1/2}}.$ 
It suffices to show that 
\be\label{show_whZ}
 \left|\|\wh Zv\|^2- n\|v\|^2\right|\prec n^{1/2} q \|v\|^2.
\ee 
In fact, provided that \eqref{show_whZ} holds, using \eqref{meanshif222} it is easy to get that 
$$ \left|\|\wt Zv\|^2- n\|v\|^2\right|\prec n^{1/2} q \|v\|^2,$$
which implies \eqref{Zv_cor} for any fixed value $c_{\varphi}$ within $(0, \frac{\varphi - 4}{2\varphi})$.

For \eqref{show_whZ}, we first observe that for $1\le i \le n$, $(\wh Zv)_i=\sum_{1\le j \le p} \wh Z_{ij}v_j$ are i.i.d random variables of mean zero and variance $\|v\|^2$. Moreover, using \eqref{eq largedev10} we get that 
$$ |(\wh Zv)_i| \prec q \max_{1\le i\le p}|v_i| + \|v\| . $$
Together with the trivial $\max_{1\le i\le p}|v_i| \le \|v\|$, this implies that the random variables $\frac{(\wh Zv)_i}{\|v\|}$, $1\le i \le p$, are i.i.d random variables of mean zero, variance 1 and bounded support $q$. Then applying \eqref{eq largedev20}, we get that
$$ \left|\|\wh Zv\|^2 - n\|v\|^2\right|=\left|\sum_i \left(|(\wh Zv)_i|^2-\E|(\wh Zv)_i|^2\right)\right|\prec n^{1/2} q  \|v\|^2 .
 $$
This concludes \eqref{show_whZ}.
 \end{proof}

@@

 \begin{corollary}\label{cor_calE}
Suppose the entries of $\cal E=[\epsilon^{(1)},\epsilon^{(2)},\cdots, \epsilon^{(t)}]\in \R^{n\times t}$ are i.i.d. random variables of mean zero, variance $\sigma^2$ and bounded moments up to any order. Then for any deterministic vector $v\in \R^n$ and deterministic $n\times n$ matrix $B\in \R^{n\times n}$, we have that with high probability,
\be\label{vcalE} |v^\top \epsilon^{(i)}| \le n^{c} \cdot \sigma \|v\|, \ee
and
\be\label{vcalA2} \left|(\epsilon^{(i)})^\top B \epsilon^{(j)} - \delta_{ij}\cdot \sigma^2 \tr(B)\right| \le n^{c}\cdot \sigma^2 \|B\|_F ,\ee
for any small constant $c>0$. As a consequence, equations \eqref{vcalE} and \eqref{vcalA2} imply that 
\be\label{vcalAE3}
\|v^\top \cal E\| \le n^{c} \cdot \sigma  \|v\|, \ \ \ \text{and}\ \ \ \left\| \cal E^\top B \cal E - \sigma^2 \tr(B)\cdot \id_{t\times t}\right\|_F \le n^{c} \cdot  \sigma^2\|B\|_F ,
\ee
 with high probability for any small constant $c>0$.
 \end{corollary}
 \begin{proof}
Note that $\epsilon^{(i)}_j/\sigma$, $1\le i \le t,1\le j \le n$, are i.i.d. random variable of mean zero, variable one and bounded moments up to any order. Then using the first estimate in equation \eqref{eq largedev1}, we can obtain that $|v^\top \epsilon^{(i)}| = \Big|\sum_{j=1}^n v_j \epsilon^{(i)}_j \Big| \prec \sigma \|v\|,$  which concludes \eqref{vcalE} together with the definition of stochastic domination in Definition \ref{stoch_domination}. Similarly, using the second estimate in equation \eqref{eq largedev1}, we can obtain that for $i\ne j$,
 \begin{align*}
\left|(\epsilon^{(i)})^\top B \epsilon^{(j)}\right| = \Big|\sum_{k,l=1}^n \epsilon^{(i)}_k\epsilon^{(j)}_l B_{kl} \Big| \prec \sigma^2 \Big(\sum_{k,l}|B_{kl}|^2\Big)^{1/2}=\sigma^2 \|B\|_F.
 \end{align*}
Using the two estimates in equation \eqref{eq largedev2}, we obtain that 
\begin{align*}
\left|(\epsilon^{(i)})^\top B \epsilon^{(j)} - \delta_{ij}\cdot \sigma^2 \tr(B)\right| &\le \Big| \sum_{k=1} \left(|\epsilon^{(i)}_k|^2-\E|\epsilon^{(i)}_k|^2\right)B_{ii} \Big|+\Big| \sum_{ k\ne l } \epsilon^{(i)}_k \epsilon^{(i)}_l B_{kl} \Big| \\
&\prec \sigma^2 \Big( \sum_{k}|B_{kk}|^2\Big)+\sigma^2 \Big( \sum_{k\ne l}|B_{kl}|^2\Big)^{1/2}\lesssim \sigma^2 \|B\|_F.
\end{align*}
The above two estimates conclude  \eqref{vcalA2}. Finally, the estimates in equation \eqref{vcalAE3} are easy consequences of equations \eqref{vcalE} and \eqref{vcalA2} since $t$ is a fixed integer that does not change with $p$.
 \end{proof}

>>>>

The following simple resolvent identities are important tools for our proof. Recall that the resolvent minors have been defined in Definition \ref{defn_Minor}, and matrix $\AF$ is given in equation \eqref{diagW}.
\begin{lemma}\label{lemm_resolvent}
We have the following resolvent identities.
\begin{itemize}
\item[(i)]
For $i\in \mathcal I_1$ and $\mu\in \mathcal I_1\cup \cal I_2$, we have
\begin{equation}
\frac{1}{G_{ii}} =  - z - \left( {\AF G^{\left( i \right)} \AF^\top} \right)_{ii} ,\quad  \frac{1}{{G_{\mu \mu } }} =  - 1  - \left( {\AF^\top  G^{\left( \mu  \right)} \AF} \right)_{\mu \mu }.\label{resolvent2}
\end{equation}

 \item[(ii)]
 For $i\in \mathcal I_1$, $\mu \in \mathcal I_1\cup \cal I_2$, $a\in \cal I\setminus \{i\}$ and $b\in \cal I\setminus \{ \mu\}$, we have
\begin{equation}
G_{ia}   = -G_{ii}  \left( \AF G^{\left( {i} \right)} \right)_{ia},\quad  G_{\mu b }  = - G_{\mu \mu }  \left( \AF^\top  G^{\left( {\mu } \right)}  \right)_{\mu b }. \label{resolvent3}
\end{equation}
%For $i\in \mathcal I_1$ and $\mu\in \mathcal I_2$, we have
%\begin{equation}\label{resolvent6}
%\begin{split}
% G_{i\mu } =  -G_{ii}  \left( WG^{\left( {i} \right)} \right)_{i\mu}, \quad G_{\mu i}= -G_{\mu\mu}\left( W^\top G^{(\mu)}\right)_{\mu i}. %\left( { - Y_{i\mu }  +  {\left( {YG^{\left( {i\mu } \right)} Y} \right)_{i\mu } } } \right) . %, \ \  G_{\mu i}  = G_{\mu \mu } G_{ii}^{\left( \mu  \right)} \left( { - Y_{\mu i}^\top  + \left( {Y^\top  G^{\left( {\mu i} \right)} Y^\top  } \right)_{\mu i} } \right).
%\end{split}
%\end{equation}

@@

\begin{fact}\label{fact_minv}
	In the setting of Theorem \ref{thm_many_tasks}, with overwhelming probability over the randomness of $X$, we have the following:
	\begin{enumerate}
		\item When $n / p$ converges to a fixed $\rho > 1$, the sample covariance matrix ${X^{\top}X} $ is of full rank.
		\item The singular values of $Z^{\top}Z$ are greater than $(\sqrt{n} - \sqrt{p})^2 - n \cdot p^{-c_{\varphi}}$ and less than $(\sqrt{n} + \sqrt{p})^2 + n \cdot p^{-c_{\varphi}}$, cf. \citet[Theorem 2.10]{isotropic} and \citet[Lemma 3.12]{DY}.
	\end{enumerate}
\end{fact}

@@

\begin{lemma}[Lemma 3.8 of \cite{EKYY1} and Theorem B.1 of \cite{Delocal}]\label{largedeviation}
Let $(x_i)$, $(y_j)$ be independent families of centered and independent random variables, and $(A_i)$, $(B_{ij})$ be families of deterministic complex numbers. Suppose the entries $x_i$ and $y_j$ have variances at most $1$, and satisfy the bounded support condition (\ref{eq_support}) for a deterministic parameter $Q$. %with $q\le n^{-\phi}$ for a small constant $\phi>0$. 
Then we have the following bounds:
%for any fixed $\xi>0$, the following bounds hold with $\xi$-high probability:
\begin{align}
\Big| \sum_{i=1}^n A_i x_i \Big\vert \prec Q \max_{i} \vert A_i \vert+ \Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad &\Big\vert  \sum_{i,j=1}^n x_i B_{ij} y_j \Big\vert \prec Q^2 B_d  + Q n^{1/2}B_o +  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}},\label{eq largedev10}  \\
\Big\vert  \sum_{i=1}^n (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec Q n^{1/2}B_d   , \quad &\Big\vert  \sum_{1\le i\ne j\le n} \bar x_i B_{ij} x_j \Big\vert  \prec Qn^{1/2}B_o +  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev20} 
\end{align}
where we denote $B_d:=\max_{i} |B_{ii} |$ and $B_o:= \max_{i\ne j} |B_{ij}|.$ Moreover, if the moments of $ x_i$ and $ y_j$ exist up to any order, then we have stronger bounds
\begin{align}
\Big\vert \sum_i A_i x_i \Big\vert \prec  \Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad  & \Big\vert \sum_{i,j} x_i B_{ij} y_j \Big\vert \prec  \Big(\sum_{i, j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev1} \\
 \Big\vert  \sum_{i} (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec  \Big( \sum_i |B_{ii} |^2\Big)^{1/2}  ,\quad & \Big\vert  \sum_{i\ne j} \bar x_i B_{ij} x_j \Big\vert  \prec \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} .\label{eq largedev2}
\end{align}
%\begin{align}
%\Big\vert \frac1{\sqrt{n}}\sum_i A_i x_i \Big\vert \prec  \frac{1}{\sqrt{n}}\Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad  & \Big\vert \frac1n\sum_{i,j} x_i B_{ij} y_j \Big\vert \prec  \frac{1}{n}\Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev1} \\
% \Big\vert  \frac1n \sum_{i} (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec \frac1{n}\Big( \sum_i |B_{ii} |^2\Big)^{1/2}  ,\quad & \Big\vert \frac1n\sum_{i\ne j} \bar x_i B_{ij} x_j \Big\vert  \prec  \frac{1}{n}\Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} .\label{eq largedev2}
%\end{align}
\end{lemma}

@@

\begin{corollary} \label{cor_largedeviation}
Let $Z\in \R^{n\times p}$ be a random matrix in the setting of Section \ref{sec_same}. Then for any deterministic vector $v\in \R^p$, we have that
\be\label{Zv_cor}\left|\|Zv\|^2- n\|v\|^2\right|\le  n^{1-c_\varphi} \|v\|^2\ee
with high probability.
\end{corollary}
 \begin{proof}
We introduce the truncated matrices $\wt Z$ with entries
$ \wt Z_{ij}:= \mathbf 1\left( |Z_{ij}|\le Q \right)\cdot Z_{ij} $
for $Q= n^{ \frac{2}{\varphi}}\log n$. By equation \eqref{Ptrunc}, we have that
\begin{equation}\label{XneX222}
\mathbb P(\wt Z= Z) =1-\OO ( (\log n)^{-\varphi}).
\end{equation}
Furthermore, by equation \eqref{meanshif} we have that
\be\label{meanshif222}
|\mathbb E  \wt  Z_{ij}| =\OO(n^{-3/2}), \quad  \mathbb E |\wt  Z_{ij}|^2 =1+ \OO(n^{-1}).
\ee
%From the first estimate in equation \eqref{meanshif}, we can also get a bound on the operator norm:
%\be\label{EZ norm222}\|\E \wt Z^{(1)}\|=\OO(n^{-1/2}) .
%\ee
Then we can centralize and rescale $\wt Z$ as $ \wh Z:=\frac{\wt Z - \E \wt Z }{ (\E|\wt Z_{11}|^2)^{1/2}}.$ 
It suffices to show that 
\be\label{show_whZ}
 \left|\|\wh Zv\|^2- n\|v\|^2\right|\prec n^{1/2} Q\|v\|^2.
\ee 
In fact, provided that \eqref{show_whZ} holds, using \eqref{meanshif222} it is easy to get that 
$$ \left|\|\wt Zv\|^2- n\|v\|^2\right|\prec n^{1/2} Q\|v\|^2,$$
which implies \eqref{Zv_cor} for any fixed value $c_{\varphi}$ within $(0, \frac{\varphi - 4}{2\varphi})$.

To prove equation \eqref{show_whZ}, we first observe that for $1\le i \le n$, $(\wh Zv)_i=\sum_{1\le j \le p} \wh Z_{ij}v_j$ are i.i.d random variables of mean zero and variance $\|v\|^2$. Moreover, using equation \eqref{eq largedev10} we get that 
$$ |(\wh Zv)_i| \prec Q\max_{1\le i\le p}|v_i| + \|v\| . $$
Together with the trivial bound $\max_{1\le i\le p}|v_i| \le \|v\|$, this implies that the random variables $\frac{(\wh Zv)_i}{\|v\|}$, $1\le i \le p$, are i.i.d random variables of mean zero, variance 1 and bounded support $Q$. Then applying equation \eqref{eq largedev20}, we get that
$$ \left|\|\wh Zv\|^2 - n\|v\|^2\right|=\left|\sum_i \left(|(\wh Zv)_i|^2-\E|(\wh Zv)_i|^2\right)\right|\prec n^{1/2} Q  \|v\|^2 .
 $$
This concludes equation \eqref{show_whZ}.
 \end{proof}

@@

 \begin{corollary}\label{cor_calE}
Suppose the entries of $\cal E=[\epsilon^{(1)},\epsilon^{(2)},\cdots, \epsilon^{(t)}]\in \R^{n\times t}$ are i.i.d. random variables of mean zero, variance $\sigma^2$ and bounded moments up to any order. Then for any deterministic vector $v\in \R^n$ and deterministic $n\times n$ matrix $B$, we have that with high probability,
\be\label{vcalE} |v^\top \epsilon^{(i)}| \le n^{c} \cdot \sigma \|v\|, \ee
and
\be\label{vcalA2} \left|(\epsilon^{(i)})^\top B \epsilon^{(j)} - \delta_{ij}\cdot \sigma^2 \tr(B)\right| \le n^{c}\cdot \sigma^2 \|B\|_F ,\ee
for any small constant $c>0$. As a consequence, equations \eqref{vcalE} and \eqref{vcalA2} imply that 
\be\label{vcalAE3}
\|v^\top \cal E\| \le n^{c} \cdot \sigma  \|v\|, \ \ \ \text{and}\ \ \ \left\| \cal E^\top B \cal E - \sigma^2 \tr(B)\cdot \id_{t\times t}\right\|_F \le n^{c} \cdot  \sigma^2\|B\|_F ,
\ee
 with high probability for any small constant $c>0$.
 \end{corollary}
 \begin{proof}
Note that $\epsilon^{(i)}_j/\sigma$, $1\le i \le t,1\le j \le n$, are i.i.d. random variable of mean zero, variable one and bounded moments up to any order. Then using the first estimate in equation \eqref{eq largedev1}, we can obtain that $|v^\top \epsilon^{(i)}| = \Big|\sum_{j=1}^n v_j \epsilon^{(i)}_j \Big| \prec \sigma \|v\|,$  which concludes \eqref{vcalE} together with the definition of stochastic domination in Definition \ref{stoch_domination}. Similarly, using the second estimate in equation \eqref{eq largedev1}, we can obtain that for $i\ne j$,
 \begin{align*}
\left|(\epsilon^{(i)})^\top B \epsilon^{(j)}\right| = \Big|\sum_{k,l=1}^n \epsilon^{(i)}_k\epsilon^{(j)}_l B_{kl} \Big| \prec \sigma^2 \Big(\sum_{k,l}|B_{kl}|^2\Big)^{1/2}=\sigma^2 \|B\|_F.
 \end{align*}
Using the two estimates in equation \eqref{eq largedev2}, we obtain that 
\begin{align*}
\left|(\epsilon^{(i)})^\top B \epsilon^{(i)} - \sigma^2 \tr(B)\right| &\le \Big| \sum_{k=1} \left(|\epsilon^{(i)}_k|^2-\E|\epsilon^{(i)}_k|^2\right)B_{ii} \Big|+\Big| \sum_{ k\ne l } \epsilon^{(i)}_k \epsilon^{(i)}_l B_{kl} \Big| \\
&\prec \sigma^2 \Big( \sum_{k}|B_{kk}|^2\Big)+\sigma^2 \Big( \sum_{k\ne l}|B_{kl}|^2\Big)^{1/2}\lesssim \sigma^2 \|B\|_F.
\end{align*}
The above two estimates conclude equation \eqref{vcalA2}. Finally, the estimates in equation \eqref{vcalAE3} are easy consequences of equations \eqref{vcalE} and \eqref{vcalA2} since $t$ is a fixed integer that does not change with $p$.
 \end{proof}
